### 2021-03-03 paper.Rmd
add application sketch

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)
- High-d shapes/distributions: normal, skewed, outliers, (Di from tutorial notes)

>>>>

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)

In single cell RNA sequencing, scientists are interested in identifying novel cell types and understanding the relationships between cells or their developmental trajectory. To achieve this they perform cluster analysis on a counts matrix or principal components and embed the results via t-SNE and label points according the cluster label. One of the main advantages of t-SNE is the avoidance of over-plotting so clusters can be clearly identified on a scatter plot, however, this can come at the cost of interpretability as global distances are distorted.  In @Laa2020-uv, we used radial transformations of the tour projections as an alternative to t-SNE that better preserves global structure while still retaining cluster topology.

- High-d shapes/distributions: normal, skewed, outliers, (Di from tutorial notes)
